\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-26 paper/mswp2012-proposal.tex
Just committing for gspot to pull
Start with UCD

\note{
\begin{itemize}
\item {\em Length: 2-5 pages}
\item {\bf How?}
\item How should the expected results be achieved?
\item What method(s) will be applied? (e.g., empirical study, user-centered design, prototype implementation,...)
\item Description of the methods.
\item Justifications for chosen methods.
\end{itemize}
}

>>>>

\subsection{User Centered Design}
We chose \emph{User Centered Design} as the procedure model used for the modern health care system. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods to emphasize functionality and robustness of systems. User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:

\begin{enumerate}
	\item Research Phase
	\item Design Phase
	\item Prototyping Phase
	\item Evaluation Phase
\end{enumerate}

\begin{figure}[htb]
	\centering
		\includegraphics[width=1\textwidth]{images/UCD.pdf}
	\caption{User Centered Design}
	\label{fig:UCD}
\end{figure}

% - Literaturrecherche - was gibt es bereits, was kann man wiederverwenden, was kann man besser machen?
% - Umfragen bei Partnern - was wird benötigt + Auswertung der Empirie
% - Usability-Tests, User-Tests
% - SW-Entwicklungsmethoden??? Wasserfall - Prototyping - oder sonst was? Gehört das hier dazu?

%\note{
%\begin{itemize}
%\item {\em Length: 2-5 pages}
%\item {\bf How?}
%\item How should the expected results be achieved?
%\item What method(s) will be applied? (e.g., empirical study, user-centered design, prototype implementation,...)
%\item Description of the methods.
%\item Justifications for chosen methods.
%\end{itemize}
%}
